\bf\mftitle

### 2011-02-23 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

\jmodule{ProjectType} is the module responsible for creation of NBP project type which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for inference.

@@

This section describes classes needed for creation of the jInfer project and correct integration into NBP. With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}, where rectangles represent folders and rounded rectangles files.\\

Main two classes representing jInfer project type are \code{JInferProjectFactory} and \code{JInferProject}. \code{JInferProjectFactory} is a factory classes responsible for creation of jInfer project from disk directory and \code{JinferProject} is represent jInfer project in NBP.

>>>>

\jmodule{ProjectType} is the module responsible for creation of NBP project type which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for inference.\\

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}, where rectangles represent folders and rounded rectangles files. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. These folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is xml file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}).

@@

This section describes classes needed for creation of the jInfer project and correct integration into NBP. Main two classes representing jInfer project type are \code{JInferProjectFactory} and \code{JInferProject}.

\subsubsection{JInferProjectFactory}

\code{JInferProjectFactory} is a factory class implementing \code{ProjectFactory} interface provided by NBP. This class is responsible for loading/saving of jInfer project from/to filesystem and also determining if folder in filesystem is type of jInfer project (contains \emph{jinferproject} subfolder). For this purpose, class has three methods: \code{isProject()}, \code{save()} and \code{load()}. When jInfer project is loaded from filesystem, \code{JInferProjectFactory} creates new instance of \code{JInferProject} passing path to project folder as a constructor parameter. When \code{save()} method is invoced, all the project properties are saved in \emph{projectproperties} file and paths to input files are saved in \emph{input.files}.

\subsubsection{JInferProject}

\code{JinferProject} class implements \code{Project} interface from NBP and represents in-memory representation of jInfer project. Inner structure of this class is very simple, interface provides only two methods: \code{getProjectDirectory()} and \code{getLookup()}. All the extensibility of project type is done by \emph{Lookup} functionality of NBP. Project lookup contains besides properties and \code{Input} class, which encapsulates input files, also class that creates output files, class that builds project tree in project window, etc.

\subsubsection{InputFiles class}\label{input.files}

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files xml file. For this purpose, class uses \emph{JAXB} architecture to unmarshall/marshall xml file into/from java content objects. Xml structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{xml}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

\noindent Example of the structure follows.
\begin{verbatim}
	<?xml version="1.0" encoding="UTF-8" standalone="yes"?>
	<jinferinput>
	    <xml>
	        <file loc="/home/user/example.xml"/>
	    </xml>
	    <schemas>
		<file loc="/home/user/example.dtd"/>
	    </schemas>
	    </queries/>
	</jinferinput>
\end{verbatim}
